\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.3in,right=0.4 in,bottom=0.3in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidt**h}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Vishal Bansal} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{Bharatpur,RJ \quad \textbf{+91 9057291541} \quad 
\href{mailto:bvansal.vb@gmail.com}{bvansal.vb@gmail.com} \\ \href{www.linkedin.com/in/vishal-bansal-62a727192/}{LinkedIN} \quad \\
\href{https://github.com/vishalbansal28}{GitHub} \quad \\ \href{https://vishal-portfolio-tawny.vercel.app/} {Website}}


\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\vspace{-3mm}
\begin{rSection}{Education}

{\bf National Institute Of Technology, Bhopal },  Bachelor of Technology \hfill {Nov 2020-April 2024}\\
Electronics and Communication Engineering     \hfill {CGPA: 7.58}

\end{rSection}
\vspace{-5mm}
%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{2ex}} l }

Technical:&APIs, Git, JavaScript, MongoDB, MySQL, NoSQL, Node.js, PostgreSQL, RESTful\\
&React, Redis, SQL, Unity, WebSocket, asynchronous programming, backend, frontend\end{tabular}\\

\vspace{-3mm}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{2ex}} l }
Soft Skills &Technical Communication, Attention to Detail, Problem Analysis, game logic, problem-solving, real-time



\end{tabular}\\
\end{rSection}
\vspace{-8mm}
\begin{rSection}{EXPERIENCE}

   \textbf{Software Backend Intern, ZuAI} \hfill Apr, 2024 - June, 2024
   \vspace{-1.5mm}
   \begin{itemize}
       \item Developed and trained AI models for data analysis and content generation, implementing algorithms to process and analyze large-scale Discord data, demonstrating strong problem-solving skills in complex data scenarios.
       \vspace{-2mm}
       \item Implemented RAG architecture and vector embeddings to enhance AI model performance, evaluating and ranking generated content quality through automated metrics and human-in-the-loop feedback.
       \vspace{-2mm}
       \item Collaborated with AI researchers to fine-tune language models, articulating complex technical concepts and contributing to model evaluation documentation with attention to detail.
   \end{itemize}
   
    \vspace{-1.5mm}
    \textbf{Software Backend Intern, ShopOut} \hfill June, 2024 -- Current
   \vspace{-1.5mm}
   \begin{itemize}
       \item Engineered an AI-powered video summarization system using advanced language models, implementing code generation techniques for automated content processing across multiple programming languages.
       \vspace{-2mm}
       \item Designed and optimized machine learning pipelines for multi-language translation, developing evaluation frameworks to assess and rank AI-generated outputs for quality and accuracy across 8 Indian languages.
       \vspace{-2mm}
       \item Led the implementation of voice synthesis models, crafting detailed technical documentation and conducting thorough code reviews to maintain high-quality standards.
   \end{itemize}
   
   \end{rSection}

  
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 \vspace{-3mm}
\begin{rSection}{PROJECTS}
\vspace{-4mm}
\item \textbf{\href{https://github.com/vishalbansal28/Business-Intelligence-Using-Deep-Learning-and-NLP}{Business Intelligence Using Deep Learning and NLP: }}{Developed machine learning models for business intelligence applications, focusing on natural language processing and deep learning techniques. Implemented model deployment pipelines and created comprehensive documentation for data analysis workflows.}\\
\textbf{Tech Stack:} Python, TensorFlow, PyTorch, NLP, Machine Learning
 \vspace{-1.5mm}
\item \textbf{\href{https://github.com/vishalbansal28/Computer-vision-image-processing}{Advanced Computer Vision Processing: }}{Implemented advanced computer vision techniques using deep learning frameworks. Developed and optimized neural network architectures for image processing tasks.}\\
\textbf{Tech Stack:} Python, TensorFlow, PyTorch, Computer Vision
 \vspace{-1.5mm}
\item \textbf{{Real-time Transcription Tool: }}{Built a live transcription system using OpenAI's GPT-3.5 for generating suggested responses from audio input. Implemented real-time processing of microphone input and speaker output.}\\
\textbf{Tech Stack:} Python, OpenAI API, FFmpeg, Audio Processing 
\vspace{-1.5mm}
\item \textbf{{Training and Fine-Tuning Large Language Models: }}{Participated in a hands-on workshop to explore training and fine-tuning large language models. Implemented practical solutions using large datasets, prompt engineering, and fine-tuning to enhance model performance.}\\ \textbf{Tech Stack:} Python, Hugging Face Transformers, PyTorch, OpenAI API, Prompt Engineering

\end{rSection} 
%----------------------------------------------------------------------------------------
   \vspace{-3mm}
\begin{rSection}{Achievements \& CERTIFICATIONS } 
\begin{itemize}
\vspace{-0.5mm}
    \item 	CodeKaze By Code Studio AIR: 331 out of 1.6 Lakh+ students and College Rank:2 
   \vspace{-2mm}
    \item	Solved over 800+ questions on DSA and SQL across platforms including \href{https://codeforces.com/profile/Bornconfusde_}{Codeforces} and
    \href{https://leetcode.com/u/bornconfusde/}{LeetCode}.
     \vspace{-2mm}
    \item Codathon By NIT Bhopal: Achieved a Rank of 431 All over India out of 6700+ students 
    \vspace{-2mm}
       \item HackerRank Problem Solving (Basic), Problem Solving (Intermediate), SQL (Basic), Python.
       \vspace{-2mm}
\item LinkedIn Skill Assessment OOPs, C++ 
\end{itemize}


\end{rSection}
   \vspace{-3mm}
%----------------------------------------------------------------------------------------
\begin{rSection}{EXTRACURRICULAR ACTIVITIES} 
\begin{itemize}
 \vspace{-0.5mm}
 \item Core Team Member Zenith, Programming Club MANIT
 \vspace{-2mm} 
 \item Sponsorship Head Maffick'23 (Cultural Fest of NIT Bhopal)
\end{itemize}


\end{rSection}


\end{document}